Optimal coordination - general experiment analysis.

### 2019-07-15 voltagebudget/analysis/exp128_analysis.Rmd
Add exp128 analysis

# Sparse exps
exp <- "127a_1"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_2"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_3"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_4"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_5"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_6"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_7"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_8"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_9"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# -
# Org dense code
# exp <- "127b"
# tmp <- NULL
# for(freq in freqs){
#   name <- paste("../../data/exp", exp, ".csv", sep="")
#   df <- read_csv(paste(name, sep=""))
#   df$freq <- rep(freq, nrow(df))
#   tmp <- rbind(tmp, df)
# }
# tmp$exp <- rep(exp, nrow(tmp))
# results <- rbind(results, tmp)
# 
# # - 
# results %>% 
#   filter(n_spikes_ref > 0) %>% 
#   # Add delta_spikes
#   mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
#   # Re-norm V_osc
#   mutate(V_osc = V_osc - V_osc_ref) -> results

@@

## Trade-off
```{r}
avg_results %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, group=interaction(exp,As))) +
  geom_line(size=1, alpha=0.6) +
  geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

>>>>

# Sparse exps
exp <- "128a_1"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "128a_2"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "128a_3"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "128a_4"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "128a_5"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "128a_6"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "128a_7"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# Org dense code
exp <- "128b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)
# 
# # - 
# results %>% 
#   filter(n_spikes_ref > 0) %>% 
#   # Add delta_spikes
#   mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
#   # Re-norm V_osc
#   mutate(V_osc = V_osc - V_osc_ref) -> results

@@

## Trade-off
```{r}
avg_results %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, group=interaction(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=exp, group=interaction(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```
